\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-07-24 manuscript/main.tex
residualization closed form done

	\begin{equation}\label{def:squared_empirical_cov}
		\widehat{\textnormal{Cov}} 
		( \langle 
		\widetilde{W},
		\xi \rangle_{\mathcal{H}}, Y )
		:=
		\frac{1}{n} 
		\sum_{i=1}^n
		y_i
		\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
		.
	\end{equation}
	We denote the estimated PLS component direction as
	\begin{equation}\label{def:maximizer_squared_empirical_cov}
		\hat{\xi} 
		= 
		(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}}
		)
		:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
		}~\widehat{\textnormal{Cov}}^2 
		\bigl(
		\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
		\bigr)~s.t.~\| \xi  \|_\mathcal{H} = 1,
	\end{equation}
	%
	where each functional part $\hat{\xi}_j $  is expanded as
	$
	\hat{\xi}_j(t) := 
	\sum_{m=1}^M \hat{\gamma}_{jm} \, b_m(t),
	$
	and $\hat{\boldsymbol{\zeta}}$ is the scalar part. This maximizer can also be represented as a Euclidean vector
	\begin{equation}\label{def:maximizer_euclidean_form}
		( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\zeta}}^\top )^\top
		\in \mathbb{R}^{MK+p},
	\end{equation}
	where the coefficient vectors $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ are defined as in \eqref{def:coef_vector_form}.
	Proposition \ref{proposition:eigen_noregul} reformulates  the problem \eqref{def:maximizer_squared_empirical_cov} as  a generalized Rayleigh quotient.
	%
	\begin{proposition}\label{proposition:eigen_noregul}
		Let
		$
		(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
		$
		denote the observed data defined in \eqref{def:problem_instance}.
		At the $l$-th iteration of the PLS algorithm, the unit-norm maximizer of  the squared empirical covariance defined in \eqref{def:maximizer_squared_empirical_cov}, represented as the Euclidean vector form as in \eqref{def:maximizer_euclidean_form},
		is obtained by solving 
		\begin{equation}	\label{eq: Unregularized generalized rayleigh quotient equation}
			\left(
			\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\zeta}}^\top
			\right)^\top
			=
			\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
			\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1.
		\end{equation}
		where
		\begin{equation}\label{def:V_matrix}
			V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)}.
		\end{equation}
	\end{proposition}
	The proof of Proposition \ref{proposition:eigen_noregul}
	is provided in Appendix \ref{section:proof:proposition:linear_regul_system_unregularized}.

@@

	\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
The $l$-th iteration's second step involves orthogonalization. This is achieved by fitting a hybrid-on-scalar regression model, where the predictor is the PLS score for each observation. The individual PLS score is computed as  $\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathcal{H}}$, utilizing the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. Subsequently, using the basis expansion coefficient notation from \eqref{def:truncated_zeta_and_delta}, \eqref{def:coef_vector_form}, \eqref{def:theta}, and \eqref{def:B_matrix}, the full vector of PLS scores $\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top$ is computed through the following matrix multiplication:
\begin{equation*}
( \hat{\boldsymbol{\rho}}^{[l]} )^\top = \sum_{k=1}^K ( \hat{\boldsymbol{\gamma}}_j^{[l]})^\top B \, (\Theta_j^{[l]})^\top + \boldsymbol{\zeta}^\top (\mathbf{Z}^{[l]}).
\end{equation*}
Using this as a scalar predictor vector, we fit the regression model $\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}_i\, \delta^{[l]} + E_i^{[l]}$, and then take the residuals as the predictor for the next iteration, namely $\widetilde{W}^{[l+1]}_i$. Here, $\delta^{[l]}$ and $E_i^{[l]}$ are the regression coefficient and error terms, respectively, both elements of $\tilde{\mathcal{H}}$ as defined in \eqref{def:truncated_hilbert_space}. To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} )$ should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}. Consequently, $\delta^{[l]}$ is obtained by minimizing a penalized least squares criterion, where the functional part is penalized by the integrated squared second derivative defined in \eqref{def:roughness_penalty}:
\begin{equation}\label{def:argmin_pensse}
	\hat{\delta}^{[l]} := \arg \min_{\delta \in \tilde{\mathcal{H}}} \operatorname{PENSSE}( \delta),
\end{equation}
where
\begin{equation}\label{def:pensse}
	\operatorname{PENSSE}( \delta)
	:=
	\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
	\,
	\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
	\rangle_{\mathcal{H}}
	+
	\tau
	\sum_{j=1}^K\operatorname{PEN}(\delta_j).
\end{equation}
The following proposition shows that the solution of the problem \ref{def:argmin_pensse} can be obtained by solving linear equations.

 \begin{proposition}[Closed-form  orthogonalization]\label{proposition:closed_form_orthgonalization}
 	asdasdasd
 \end{proposition}
 Proof of Proposition \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.
%Using the basis expansion coefficient notation presented in \eqref{def:truncated_zeta_and_delta} and \eqref{def:coef_vector_form}, \eqref{def:theta}, \eqref{def:B_matrix}
\jongmin{Old writing starts here. I temporarily mixed the order of the paragraphs.}
%As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$. Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \boldsymbol{\gamma}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\boldsymbol{\gamma}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients. Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}. With the $(MK+p)$-dimensional row vector $\boldsymbol{\gamma}^* = (\boldsymbol{\gamma}^{(1)\top}, \ldots, \boldsymbol{\gamma}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: 
$\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}]$. Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
\begin{equation}
	\widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
	\label{eq: rewritten hybrid on scalar regression model}
\end{equation}
$\mathbf{e}[\mathbf{t}]$ is an $n \times (K+p)$ matrix of errors. 
\\

	Based on the model formulation \eqref{eq: rewritten hybrid on scalar regression model}, we can now formulate the following least squares criterion whose minimizing solution gives the estimate of the regression coefficient $\boldsymbol{\delta}[\mathbf{t}]$ in the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model}:
\begin{equation}
	\begin{aligned}
		\textnormal{SSE}(\delta) &= \int_\mathcal{T} \left\Vert \,  \widetilde{C}^* B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] \, \right\Vert_F^2 \, d\mathbf{t}  \\
		&= tr\left(\widetilde{C}^{*T}\widetilde{C}^*J^\ast \right) - 2\,tr \left(\boldsymbol{\gamma}^* J^\ast \widetilde{C}^{*T} \widehat{\boldsymbol{\rho}} \right) + tr\left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* J^\ast \boldsymbol{\gamma}^{*T}\right),
	\end{aligned}
	\label{eq: least squares}
\end{equation}
where $tr$ denotes the trace of a matrix, and $\Vert \cdot \Vert_F$ is a Frobenius norm. Now taking the derivative of \eqref{eq: least squares} with respect to $\boldsymbol{\gamma}^*$ and setting the result to zero, we find that  $\boldsymbol{\gamma}^*$ satisfies the system of linear equations
\begin{equation*}
	\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^*  J^\ast =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast,
\end{equation*}
whose solutions lead to the following estimates of $\boldsymbol{\gamma}^*$ and $\boldsymbol{\delta}[\mathbf{t}]$:
\begin{equation*}
	\widehat{\boldsymbol{\gamma}}^*  =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast \left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} J^\ast \right)^{-1} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \, \widehat{\boldsymbol{\gamma}}^{*\top}.
\end{equation*}
Then, we can use $\widehat{\boldsymbol{\delta}}[\mathbf{t}]$ to obtain the subsequent residualized hybrid predictor as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$.

@@

		\section{Proof of Proposition \ref{proposition:eigen_regul} }\label{section:proof:proposition:eigen_regul}
		The penalization term 
		$\sum \limits_{j=1}^K \lambda_j 
		\operatorname{PEN}(\xi_K)$
		can be written in matrix form as:
		\begin{align*}
			\sum \limits_{j=1}^K 
			\lambda_j
			\operatorname{PEN}({\xi}_j)
			&=
			\sum \limits_{j=1}^K 
			\lambda_j
			\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
			\\&=
			\sum \limits_{j=1}^K 
			\lambda_j
			\int_0^1 \bigl\{ \sum_{l=1}^M \theta_{ijl} \, b_l^{\prime \prime}(t) \bigr\}^2 dt
			\\&	 =
			%%%%%%%%%%%%%%%%%%%
			\sum \limits_{j=1}^K 
			\lambda_j
			\sum_{l=1}^M
			\sum_{m=1}^M
			\theta_{ijl} \theta_{ijm}
			\int_0^1
			\, b_l^{\prime \prime}(t) 
			b_m^{\prime \prime}(t)
			dt
			\\&	 =
			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
			\sum \limits_{j=1}^K
			\lambda_j
			\boldsymbol{\gamma}_j^\top
			B^{\prime \prime} 
			\boldsymbol{\gamma}_j
			%%%%%%%%%%%%%%%%%%%%%%%%%%
			\\&= 
			\boldsymbol{\xi}^{\top} \Lambda \mathbb{B}^{\prime \prime} \boldsymbol{\xi},
		\end{align*}
		where $\boldsymbol{\xi}$ is the concatenated coefficient vector form of $\xi$ as defined in \eqref{def:maximizer_euclidean_form}, $\mathbb{B}^{\prime\prime}$ is defined in \eqref{def:gram_block}, and $\Lambda$ is defined in \eqref{def:Lambda}.

@@

	\section{Proof of Proposition \ref{proposition:closed_form_orthgonalization} \ref{}}\label{section:proof:proposition:closed_form_orthgonalization}
	 \begin{align*}
		\operatorname{PENSSE}( \delta)
		&=
		\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
		\,
		\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
		\rangle_{\mathcal{H}}
		+
		\tau
		\sum_{j=1}^K\operatorname{PEN}(\delta_j) 
		%%%%%%%%%%%%%%%%%%%%
		\\&=
		\sum_{i=1}^n 
		\langle \widetilde{W}_i^{[l]},  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
		-
		\sum_{i=1}^n 
		\hat{\rho}_i^{[l]} 
		\langle \delta,  \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}
		+
		\bigl(
		\sum_{i=1}^n 
		( \hat{\rho}_i^{[l]} )^2
		\bigr)
		\langle \delta,  \, \delta \rangle_{\mathcal{H}}
		+
		\tau
		\sum_{j=1}^K\operatorname{PEN}(\delta_j) 
		\\&=
		\operatorname{tr}(C^{*T} C^{*}J^{*}\Lambda) 
		- 
		2 \operatorname{tr}(d^{*}J^{*}C^{*T} \rho\Lambda) 
		+
		\rho^T \rho
		\operatorname{tr}( d^{*}J^{*}d^{*T} \Lambda) + \tau \operatorname{tr}(\ddot{d}^{*}J^{*}\ddot{d}^{*T}) \jongmin{need to be fixed}
	\end{align*}

	\section{Proof of Proposition \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}
	$\mathcal{U}$ is \textit{positive} because for every $\mathbf{h} \in \mathcal{H}$,
	\begin{equation*}
		\langle \mathcal{U} \mathbf{h}, \mathbf{h} \rangle_\mathcal{H} = \langle \langle \Sigma_{YW}, \mathbf{h} \rangle_{\mathcal{H}} \, \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}^2 \ge 0.
	\end{equation*}

>>>>

	\begin{equation}\label{def:squared_empirical_cov}
		\widehat{\textnormal{Cov}} 
		( \langle 
		\widetilde{W},
		\xi \rangle_{\mathcal{H}}, Y )
		:=
		\frac{1}{n} 
		\sum_{i=1}^n
		y_i
		\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
		.
	\end{equation}
	We denote the estimated PLS component direction as
	\begin{equation}\label{def:maximizer_squared_empirical_cov}
		\hat{\xi} 
		= 
		(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}}
		)
		:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
		}~\widehat{\textnormal{Cov}}^2 
		\bigl(
		\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
		\bigr)~s.t.~\| \xi  \|_\mathcal{H} = 1,
	\end{equation}
	%
	where each functional part $\hat{\xi}_j $  is expanded as
	$
	\hat{\xi}_j(t) := 
	\sum_{m=1}^M \hat{\gamma}_{jm} \, b_m(t),
	$
	and $\hat{\boldsymbol{\zeta}}$ is the scalar part. This maximizer can also be represented as a concatenated Euclidean vector
	\begin{equation}\label{def:maximizer_euclidean_form}
		( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\zeta}}^\top )^\top
		\in \mathbb{R}^{MK+p},
	\end{equation}
	where the coefficient vectors $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ are defined as in \eqref{def:coef_vector_form}.
	Proposition \ref{proposition:eigen_noregul} reformulates  the problem \eqref{def:maximizer_squared_empirical_cov} as  a generalized Rayleigh quotient.
	%
	\begin{proposition}\label{proposition:eigen_noregul}
		Let
		$
		(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
		$
		denote the observed data defined in \eqref{def:problem_instance}.
		At the $l$-th iteration of the PLS algorithm, the unit-norm maximizer of  the squared empirical covariance defined in \eqref{def:maximizer_squared_empirical_cov}, represented as the Euclidean vector form as in \eqref{def:maximizer_euclidean_form},
		is obtained by solving 
		\begin{equation}	\label{eq: Unregularized generalized rayleigh quotient equation}
			\left(
			\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\zeta}}^\top
			\right)^\top
			=
			\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
			\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1.
		\end{equation}
		where
		\begin{equation}\label{def:V_matrix}
			V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)}.
		\end{equation}
	\end{proposition}
	The proof of Proposition \ref{proposition:eigen_noregul}
	is provided in Appendix \ref{section:proof:proposition:linear_regul_system_unregularized}.

@@

	\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
The $l$-th iteration's second step involves orthogonalization. This is achieved by fitting a hybrid-on-scalar regression model, where the predictor is the PLS score for each observation. The individual PLS score is computed as  
\begin{equation}\label{def:plsscore}
\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathcal{H}},
\end{equation}
 utilizing the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
Using this as a scalar predictor observations, we fit the regression model $\widetilde{W}^{[l]}_i = \hat{\rho}^{[l]}_i\, \delta^{[l]} + E_i^{[l]}$, and then take the residuals as the predictor for the next iteration, namely $\widetilde{W}^{[l+1]}_i$. Here, $\delta^{[l]}$ and $E_i^{[l]}$ are the regression coefficient and error terms, respectively, both elements of $\tilde{\mathcal{H}}$ as defined in \eqref{def:truncated_hilbert_space}. To ensure the stability of the entire PLS estimation procedure, the estimated regression coefficient $\hat{\delta}^{[l]} = (\hat{\delta}^{[l]}_1, \ldots, \hat{\delta}^{[l]}_K, \hat{\boldsymbol{\chi}}^{[l]} ) \in \tilde{\mathcal{H}}$, should have smooth functional parts, consistent with Section \ref{sec: Regularization of PLS Components}. Consequently, $\delta^{[l]}$ is obtained by minimizing a penalized least squares criterion, where the functional part is penalized by the integrated squared second derivative defined in \eqref{def:roughness_penalty}:
\begin{equation}\label{def:argmin_pensse}
	\hat{\delta}^{[l]} := \arg \min_{\delta \in \tilde{\mathcal{H}}} \operatorname{PENSSE}( \delta),
\end{equation}
where
\begin{equation}\label{def:pensse}
	\operatorname{PENSSE}( \delta)
	:=
	\sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta,
	\,
	\widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta
	\rangle_{\mathcal{H}}
	+
	\tau
	\sum_{j=1}^K\operatorname{PEN}(\delta_j).
\end{equation}
The following proposition shows that the solution of the problem \ref{def:argmin_pensse} can be obtained by solving linear equations.

 \begin{proposition}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
 	Let us denote
 	\begin{equation*}
 		 		\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top
 	\quad\text{and} \quad
 			\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}
 	\end{equation*}
 	The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
 	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients and scalar parts given by:
\begin{equation*}
	\hat{\boldsymbol{\pi}}_j^{[l]}
	=
	\bigl(
		\bar{\rho}^{[l]}
  B
	+
	\tau
	B^{\prime \prime}
	\bigr)^{-1}
	  B
	(\Theta_j^{[l]})^\top,
	~
	j = 1, \ldots, K,
	%%%%%%%%%%%%%%%%%%%%%%%%
	\quad
	\hat{\boldsymbol{\chi} }
	=
	(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}.
\end{equation*}
 \end{proposition}
 Proof of Proposition \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.

 Now we formally state the orthogonalization step.

%Using the basis expansion coefficient notation presented in \eqref{def:truncated_zeta_and_delta} and \eqref{def:coef_vector_form}, \eqref{def:theta}, \eqref{def:B_matrix}
\jongmin{Old writing starts here. I temporarily mixed the order of the paragraphs.}
Then, we can use $\widehat{\boldsymbol{\delta}}[\mathbf{t}]$ to obtain the subsequent residualized hybrid predictor as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$.

@@

		\section{Proof of Proposition \ref{proposition:eigen_regul} }\label{section:proof:proposition:eigen_regul}
		The penalization term 
		$\sum \limits_{j=1}^K \lambda_j 
		\operatorname{PEN}(\xi_K)$
		can be written in matrix form as:
		\begin{align*}
			\sum \limits_{j=1}^K 
			\lambda_j
			\operatorname{PEN}({\xi}_j)
			&=
			\sum \limits_{j=1}^K 
			\lambda_j
			\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
			\\&=
			\sum \limits_{j=1}^K 
			\lambda_j
			\int_0^1 \bigl\{ \sum_{l=1}^M \theta_{ijl} \, b_l^{\prime \prime}(t) \bigr\}^2 dt
			\\&	 =
			%%%%%%%%%%%%%%%%%%%
			\sum \limits_{j=1}^K 
			\lambda_j
			\sum_{l=1}^M
			\sum_{m=1}^M
			\theta_{ijl} \theta_{ijm}
			\int_0^1
			\, b_l^{\prime \prime}(t) 
			b_m^{\prime \prime}(t)
			dt
			\\&	 =
			%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
			\sum \limits_{j=1}^K
			\lambda_j
			\boldsymbol{\gamma}_j^\top
			B^{\prime \prime} 
			\boldsymbol{\gamma}_j
			%%%%%%%%%%%%%%%%%%%%%%%%%%
			\\&= 
			\boldsymbol{\xi}^{\top} \Lambda \mathbb{B}^{\prime \prime} \boldsymbol{\xi},
			\numberthis \label{pen_as_matrix}
		\end{align*}
		where $\boldsymbol{\xi}$ is the concatenated coefficient vector form of $\xi$ as defined in \eqref{def:maximizer_euclidean_form}, $\mathbb{B}^{\prime\prime}$ is defined in \eqref{def:gram_block}, and $\Lambda$ is defined in \eqref{def:Lambda}.

@@

\section{Proof of Proposition \ref{proposition:closed_form_orthgonalization} }\label{section:proof:proposition:closed_form_orthgonalization}
For notational simplicity, we omit the iteration superscript $[l]$.
	Using the basis expansion coefficient notation from \eqref{def:truncated_zeta_and_delta}, \eqref{def:coef_vector_form}, \eqref{def:theta}, and \eqref{def:B_matrix}, the full vector of PLS scores $\hat{\boldsymbol{\rho}}  = (\hat{\rho}_1, \ldots, \hat{\rho}_n)^\top$ 
	where
	$\hat{\rho}_1$ is defined in \eqref{def:plsscore},
	is computed through the following matrix multiplication:
	\begin{equation*}
		 \hat{\boldsymbol{\rho}}^\top = \sum_{k=1}^K ( \hat{\boldsymbol{\gamma}}_j )^\top B \, \Theta_j^\top + \boldsymbol{\zeta}^\top \mathbf{Z}^\top.
	\end{equation*}
The criterion $\operatorname{PENSSE}( \delta)$ can be decomposed as follows:

\begin{align*}
	\operatorname{PENSSE}( \delta) &= \sum_{i=1}^n \langle \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta, \, \widetilde{W}_i^{[l]} - \hat{\rho}_i^{[l]}\, \delta \rangle_{\mathcal{H}} + \tau \sum_{j=1}^K\operatorname{PEN}(\delta_j) \\
	&= 
	\underbrace{
		\sum_{i=1}^n \langle \widetilde{W}_i^{[l]}, \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}}}_{A} 
	\underbrace{
		-2 \sum_{i=1}^n \hat{\rho}_i^{[l]} \langle \delta, \, \widetilde{W}_i^{[l]} \rangle_{\mathcal{H}} 
	}_{B_1(\boldsymbol{\delta})}
	\underbrace{
		+ 
		(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})
		 \langle \delta, \, \delta \rangle_{\mathcal{H}}
	}_{B_2(\boldsymbol{\delta})}
	\underbrace{
		 + 
		 \tau \sum_{j=1}^K\operatorname{PEN}(\delta_j)
	}_{B_3(\boldsymbol{\delta})}
\end{align*}
Here, part $A$ does not contain $\delta$, so it does not contribute to the minimization problem.

Let $\boldsymbol{\delta}:= (\pi_1^\top, \ldots, \pi_K^\top, \boldsymbol{\chi}^\top )^\top$ be the $MK+p$-dimensional concatenated vector of basis coefficients and the scalar part of $\boldsymbol{\delta}$, as presented in \eqref{def:maximizer_euclidean_form}. 
Abusing notation, we treat $\operatorname{PENSSE}$ as a function of $\boldsymbol{\delta}$.
Next, We will now demonstrate that the combined term $
B_1(\boldsymbol{\delta}) + B_2(\boldsymbol{\delta}) + B_3(\boldsymbol{\delta})
$ is a quadratic function of $\boldsymbol{\delta}$, by expanding its component functions:
	B_1(\boldsymbol{\delta}) &= 
	- 2\sum_{i=1}^n \hat{\rho}_i  \langle \delta, \, \widetilde{W}_i  \rangle_{\mathcal{H}} 
	- 2\hat{\boldsymbol{\rho}}^\top 
	\sum_{j=1}^K \Theta_j B \boldsymbol{\pi}_j
	+\mathbf{Z} \boldsymbol{\chi}
	\biggr),
%%%%%%%%%%%%%%%%%%%%%%%
	B_2(\boldsymbol{\delta})
	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})
	\langle \delta, \, \delta \rangle_{\mathcal{H}}
	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
	\sum_{j=1}^K \pi_j^\top B \pi_j
	+\boldsymbol{\chi}^\top \boldsymbol{\chi}
	\biggr),
	B_3(\boldsymbol{\delta})
	\tau \sum_{j=1}^K\operatorname{PEN}(\delta_j)
	\tau
	\boldsymbol{\delta} B^{''} \boldsymbol{\delta},
where the expansion of $B_3(\boldsymbol{\delta})$ leverages the computation in \eqref{pen_as_matrix}.
Now we compute the gradients:
		\nabla_{\boldsymbol{\pi}_j}
		 B_1(\boldsymbol{\delta}) 
		 &= -2
		 \Theta_j^\top
		 \hat{\boldsymbol{\rho}}  ,~
		  j = 1, \ldots, K,
			\nabla_{\boldsymbol{\chi}}
	B_1(\boldsymbol{\delta}) 	  
	= -2\mathbf{Z}^\top  \hat{\boldsymbol{\rho}},
	\nabla_{\boldsymbol{\pi}_j}
	B_2(\boldsymbol{\delta}) 
	2
	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
	B 	\boldsymbol{\pi}_j
	,~
	j = 1, \ldots, K,
	\nabla_{\boldsymbol{\chi}}
	B_2(\boldsymbol{\delta}) 
	2\boldsymbol{\chi} ,
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\nabla_{\boldsymbol{\pi}_j}
	B_3(\boldsymbol{\delta}) 
	2 \tau
	B^{\prime \prime }	\boldsymbol{\pi}_j
	,~
	j = 1, \ldots, K,
	\nabla_{\boldsymbol{\chi}}
	B_3(\boldsymbol{\delta}) 
0.
The Hessian of 
$\operatorname{PENSSE}( \boldsymbol{\delta})$ is then given by 
2 	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})  B
2
\tau
 B^{\prime \prime}.
Since we assumed in Section \ref{sec: finite basis approximation} that both $B'$ and $B''$ are positive definite, $\operatorname{PENSSE}( \delta)$ is convex. convex. Consequently, the gradient vanishes at its unique minimizer:
	\nabla_{\boldsymbol{\pi}_j}	\operatorname{PENSSE}( \hat{\boldsymbol{\delta}} )
	 -2
	\Theta_j^\top
	\hat{\boldsymbol{\rho}}
2	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}}) 
B 	\hat{\boldsymbol{\pi}}_j
		2
	B^{\prime \prime }	\hat{\boldsymbol{\pi}}_j
	0,~
	j = 1, \ldots, K,
	\nabla_{\boldsymbol{\chi} }	\operatorname{PENSSE}( \hat{\boldsymbol{\delta}} )
-2\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}
2\hat{\boldsymbol{\chi} }
0,
providing the following closed-form solution:
	\hat{\boldsymbol{\pi}}_j\\
	(\hat{\boldsymbol{\rho}}^\top \hat{\boldsymbol{\rho}})  B
	\tau
	B^{\prime \prime}
	\bigr\}^{-1}
\Theta_j^\top
j = 1, \ldots, K,
	%%%%%%%%%%%%%%%%%%%%%%%%
\hat{\boldsymbol{\chi} }
=\mathbf{Z}^\top  \hat{\boldsymbol{\rho}}.
This completes the proof of Proposition \ref{proposition:closed_form_orthgonalization}.
	\section{Proof of Proposition \ref{Proposition: property of U}}\label{section:proof:Proposition: property of U}
	$\mathcal{U}$ is \textit{positive} because for every $\mathbf{h} \in \mathcal{H}$,
		\langle \mathcal{U} \mathbf{h}, \mathbf{h} \rangle_\mathcal{H} = \langle \langle \Sigma_{YW}, \mathbf{h} \rangle_{\mathcal{H}} \, \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}^2 \ge 0.
